Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-05-24 paper/AlignedIsotropicGW.tex
Close #32 by adding forward reference to generalised 'low' distribution.

Most of our resolving power for the spin angular distribution is a
result of the fact that our ``aligned'' models cannot produce
$\chieff < 0$ (see Figure \ref{fig:chieff-distribution-models}).  If
spins are intrinsically very small, with $a \lesssim 0.3$, then it is
no longer possible to resolve the negative effective spin with a small
number of observations.  As noted below, however, spins observed in
X-ray binaries are typically large.  Additionally, models which do not
permit \emph{some} spins with $\chieff \gtrsim 0.1$ are ruled out by
the GW151226 observations\cite{2016PhRvL.116x1103A}.  An ``aligned''
model with spin magnitudes from our ``flat'' distribution but
permitting spin vectors oriented anti-parallel to the orbital angular
momentum (leading to the possibility of positive \emph{or} negative
$\chieff$) can only be distinguised from an isotropic true population
at $\sim 3 \sigma$ after 10--20
observations\cite{2017CQGra..34cLT01V}; our flat aligned model can be
distinguished from such a population at better than $5\sigma$ (odds
$< 10^{-8}$) after 10 observations, emphasising the information
content of the bound $\chieff > 0$ for our aligned models.

>>>>

Most of our resolving power for the spin angular distribution is a
result of the fact that our ``aligned'' models cannot produce
$\chieff < 0$ (see Figure \ref{fig:chieff-distribution-models}).  If
spins are intrinsically very small, with $a \lesssim 0.3$, then it is
no longer possible to resolve the negative effective spin with a small
number of observations (see Methods Section \ref{sec:smallspins}).  As
noted below, however, spins observed in X-ray binaries are typically
large.  Additionally, models which do not permit \emph{some} spins
with $\chieff \gtrsim 0.1$ are ruled out by the GW151226
observations\cite{2016PhRvL.116x1103A}.  An ``aligned'' model with
spin magnitudes from our ``flat'' distribution but permitting spin
vectors oriented anti-parallel to the orbital angular momentum
(leading to the possibility of positive \emph{or} negative $\chieff$)
can only be distinguised from an isotropic true population at
$\sim 3 \sigma$ after 10--20 observations\cite{2017CQGra..34cLT01V};
our flat aligned model can be distinguished from such a population at
better than $5\sigma$ (odds $< 10^{-8}$) after 10 observations,
emphasising the information content of the bound $\chieff > 0$ for our
aligned models.
